\documentclass{article}
\usepackage{gvv-book}
\usepackage{gvv}
\begin{document}

\section*{Eighth International Olympiad, 1966}

\subsection*{19661.}
In a mathematical contest, three problems, $A, B, C$ were posed. Among the participants there were 25 students who solved at least one problem each. Of all the contestants who did not solve problem $A$, the number who solved $B$ was twice the number who solved $C$. The number of students who solved only problem $A$ was one more than the number of students who solved $A$ and at least one other problem. Of all students who solved just one problem, half did not solve problem $A$. How many students solved only problem $B$?

\subsection*{1966/2.}
Let $a, b, c$ be the lengths of the sides of a triangle, and $\alpha, \beta, \gamma$, respectively, the angles opposite these sides. Prove that if
\begin{align*}
a + b = \tan \frac{\gamma}{2} (a \tan \alpha + b \tan \beta),
\end{align}
the triangle is isosceles.

\subsection*{1966/3.}
Prove: The sum of the distances of the vertices of a regular tetrahedron from the center of its circumscribed sphere is less than the sum of the distances of these vertices from any other point in space.

\subsection*{1966/4.}
Prove that for every natural number $n$, and for every real number $x \neq k\pi/2^t$ $(t = 0, 1, \ldots, n; k$ any integer$)$
$$
\frac{1}{\sin 2x} + \frac{1}{\sin 4x} + \cdots + \frac{1}{\sin 2^n x} = \cot x - \cot 2^n x.
$$

\subsection*{1966/5.}
Solve the system of equations
\begin{align*}
|a_1 - a_2|x_2+|a_1 - a_3|x_3+|a_1 - a_4|x_4=1 \\
|a_2 - a_1|x_1+|a_2 - a_3|x_3+|a_2 - a_4|x_4=1 \\
|a_3 - a_1|x_1+|a_3 - a_2|x_2+|a_3 - a_4|x_4=1 \\
|a_4 - a_1|x_1+|a_4 - a_2|x_2+|a_4 - a_3|x_3=1
\end{align*}
where $a_1, a_2, a_3, a_4$ are four different real numbers.

\subsection*{1966/6.}
In the interior of sides $BC, CA, AB$ of triangle $ABC$, any points $K, L, M$, respectively, are selected. Prove that the area of at least one of the triangles $AML, BKM, CLK$ is less than or equal to one quarter of the area of triangle $ABC$.

\end{document}
